% Preamble
% ---
\documentclass[11pt,a4paper,roman]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\usepackage[scale=0.79]{geometry}
\renewcommand{\baselinestretch}{1.1}

% Personal data
% ---
\name{James}{Ravn}
\title{Software Engineer}
\phone{+44 07463 500595}
\email{james@r-vn.org}
\homepage{www.jsravn.com}
\social[linkedin]{jsravn}
\social[github]{jsravn}

% Content
% ---
\begin{document}
\makecvtitle{}

\section{About}
\begin{itemize}
  \item Software engineer with 15 years of experience in software development and technical leadership.
  \item In depth knowledge of infrastructure automation and building platforms in the cloud (AWS/GCP).
  \item Able to run projects and manage the software life cycle from start to production.
  \item Primarily interested in distributed systems, infrastructure automation, and systems programming.
\end{itemize}

\section{Experience}

\cventry{2020--Current}{Principal Consultant}{\href{https://cecg.io}{CECG}}{London, UK}{}{}
\begin{itemize}
  \item As one of the first consultants of CECG, a boutique consulting firm specializing in infrastructure and
        platforms, I have been engaged with Sky/NBCU to provide technical and leadership expertise for the core engineering
        platform.  It supports hundreds of software teams globally and hosts Sky OVP and NBCU Peacock services.
  \item Design and implementation of the GCP based core platform. (Pulumi, Go, Typescript, K8s)
\end{itemize}

\vspace{5mm}

\cventry{2018--2020}{Tech Lead / Principal Software Engineer}{\href{https://lightbend.com}{Lightbend}}{London, UK}{}{}
\begin{itemize}
  \item Tech lead for Lightbend Console, a monitoring product built for Akka/Play/Lagom. Led
        team of 5 engineers. (Prometheus, K8s, Go, Scala)
  \item Principal software engineer in the Office of the CTO.\@ Worked on cloudstate.io, a managed Akka serverless platform.
        (GCP, K8s, Go, Scala, Akka)
\end{itemize}

\vspace{5mm}

\cventry{2014--2018}{Principal Software Engineer}{\href{http://www.sky.uk}{Sky}}{London, UK}{}{}
\begin{itemize}
  \item Co-created the core engineering team for Sky's commerce and online video platforms.
  \item Advocated for, architected and implemented a common development platform and CI/CD process built on
        Kubernetes. The platform is built as a PaaS and deployed daily into production. This platform has
        grown to support the majority of Sky and NBCU online services including Peacock. It hosts hundreds
        of development teams and consists of clusters with hundreds of nodes, with production peaks routing
        200k-300k requests per second. (Golang, Terraform, Ansible, AWS, Jenkins, Gradle)
  \item Kubernetes contributor to support our efforts with several dozen contributions and improvements,
        particularly in the areas of storage and scalability. Also created and contributed to related
        open source projects, including feed (ingress controller), fluent-bit, merlin (IPVS manager),
        etcd-bootstrapper (500k+ downloads), and cqlmigrate (Cassandra schema migrations). (Golang, C)
\end{itemize}

\vspace{5mm}

\cventry{2014--2016}{Software Consultant}{Energized Work}{London, UK}{}{}
\begin{itemize}
\item Consultant for EW, a boutique software consultancy specializing in XP, Agile, and software delivery.
\end{itemize}

\vspace{5mm}

\cventry{2013--2014}{Senior Software Engineer}{Camelot}{London, UK}{}{}
\begin{itemize}
  \item Worked on the next generation lottery platform for the UK.\@ I made significant contributions
        to the subscriptions component, considered the most complex part of the code base. It serves
        over 1 million users with direct debit using BACS.\@ (Java, Spring, Gradle, Grails)
  \item Heavily involved in devops, I advocated and implemented the branching and code review process,
        rescuing a very broken build process to get >90\% green builds from a 10\% rate when I joined.
        (Puppet, gitlab, Jenkins)
\end{itemize}

\vspace{5mm}

\cventry{2009--2013}{Senior Software Engineer}{\href{www.imc.nl}{IMC Financial Markets}}{Chicago, IL}{}{}
\begin{itemize}
\item Senior engineer on automated trading team. Top ranked by management and peers.
\item Designed and implemented the core valuation library and parameter server, leveraged across the firm for pricing of derivatives.
  \begin{itemize}
    \item Enabled new strategies and enhanced existing ones with significant contribution to PnL. It
          consolidated many separate, fragmented components used by different trading desks.
    \item Implemented in core Java with minimal dependencies and high concurrency, utilizing Java
          concurrency primitives.
    \item Novel design built using Java annotated classes and graph analysis to build a pricing DAG.\@
          Cucumber specs for building acceptance criteria of specific pricing combinations.
    \item High performance server component for persisting and propagating parameters of the pricing models.
          Created custom Mongo Java driver to enable high throughput. (Java, ActiveMQ, Mysql/Mongo)
  \end{itemize}
  \item Replaced the company wide ant-based build system with Maven, leading to an 80\%
        reduction in build times and significant code reduction. This had a large impact on developer
        productivity.
  \item Performance improvements to the primary feed component which groups orders and has significant
        state, increasing capacity from 2 million to \textgreater{} 30 million orders per minute.
\item Developed jabber bot and accompanying pidgin plugin in C to support broker traders over chat.
\item Mentored junior developers, hosted book clubs, and brown bag lunches on various topics.
\end{itemize}

\vspace{5mm}

\cventry{2006--2009}{Senior Software Engineer}{\href{www.motorola.com}{Motorola}}{Libertyville, IL}{}{}
\begin{itemize}
\item Consistently ranked in the top 10\% of company employees.
  \item Designed novel software delivery estimation model that became the de facto estimation tool for the mobile
        software organization due to its simplicity and usefulness, utilizing a combination of linear regression and
        Markov chains on historical data. (Excel/VBA)
  \item Lead developer of software quality website used by software management, which provided multiple data aggregation
        and analysis models from various disparate sources. This led to significant improvements in delivery estimation
        and resource allocation. (ASP.NET)
  \item Implemented defect triage web tool which improved turnaround time for bug fixes. (Rails)
\end{itemize}

\section{Education}
\cventry{2021}{M.S. Computer Science, Computing Specialization}{\href{http://www.gatech.edu}{Georgia Tech}}{\textit{4.0}}{}{Courses included distributed computing, high performance computing, and binary exploitation.}
\cventry{2005}{B.S. Computer Science and Engineering}{\href{http://engineering.ucla.edu}{University of California, Los Angeles}}{}{}{}

\end{document}
